---
title: \vspace{3in}Accounting Report 2019 Example Report with Randomized Numbers
author:   Robert Schnitman
date: '`r gsub("0[0-9],", paste0(substr(format(Sys.Date(), "%B %d, %Y"), 11, 11), ","), format(Sys.Date(), "%B %d, %Y"))`'
output:
 pdf_document:
   toc: true
   includes:
     before_body: tex\ar19_beforebody.tex
     #in_header: ar19_hf.tex
     
 header-includes:
   - \usepackage{fancyhdr}
   - \usepackage{lastpage}
   - \usepackage{xcolor}
---



\newpage

```{r parameters, include = FALSE}
##### === EDIT PARAMETERS AS NECESSARY === #####

#### SET YEAR AND FILE NAME####
yr <- 2019

myfile <- 'transactions4.xls'

#### SET INCOME & EXPENSE GOALS
plan_inc <- 36000/12 # Monthly livable income goal
plan_exp <- (plan_inc/3) # Ideal expenses allocation.

#### LOAD LIBRARIES ####
#libs <- c('readxl', 'tidyr', 'knitr', 'ggplot2', 'kableExtra', 'lattice')
libs <- c('readxl', 'tidyverse', 'knitr', 
          'kableExtra', 'lattice', 'grid', 
          'gridExtra', 'magrittr')
lapply(libs, library, character.only = TRUE)

# SciencesPo was depcrecated...

```

```{r SETUP, include = FALSE}
##### === SET UP === #####
set.seed(1)
#### SET WORKING DIRECTORY ####
setwd("~/MEGA/Personal/Money/")

#### READ DATA ####
  
for (i in c('income', 'expenses', 'investments')) {
  
  assign(paste(substr(i, 1, 3), 'df', sep = '.'), 
         subset(read_excel(myfile, sheet = i), year == yr))
  
}

map_rand <- function(x) map_df(x, ~ .x*rnorm(length(.x)))

inc.df[, 16:21] %<>% map_rand()
exp.df[, 9:15] %<>% map_rand()
inv.df[, 8] %<>% map_rand()
  
```

```{r list_setup, echo = FALSE}


### General Functions.

## Using "colnames" due to some objects being matrices instead of data frames.
not_date  <- function(data) !grepl('date|month', colnames(data), ignore.case = TRUE)
not_total <- function(data) !grepl('total', colnames(data), ignore.case = TRUE)

mapc <- function(f, x, ...) apply(x, 2, f, ...)
mapr <- function(f, x, ...) apply(x, 1, f, ...)

# nd = "Not Date" (calculate everything except the "Total" column)
mapr_dt <- function(data, f) apply(data[, not_date(data)], 1, f, na.rm = TRUE) 

# nt = "Not Total" (calculate everything except the "Total" column)
mapr_nt <- function(data, f) apply(data[, not_total(data)], 1, f, na.rm = TRUE) 

mapnum <- function(f, x, ...) {
  
  if (typeof(x) != 'list') {
    
    x <- as.data.frame(x)
    
  }
  
  rapply(x, f, classes = 'numeric', na.rm = TRUE)
  
  
}


### Reporting Functions
mark.list <- list(big.mark = ',', small.mark = '.') # For kable() 

## for ordering month as first.
# This was created before the note_date() function. Kept for legacy purposes.
not_month <- function(df) {names(df)[!grepl('month|Month', names(df))]} 

#NAto0df   <- function(df) {as.data.frame(replace(x = df, list = is.na(df), 0))} # For easier calculations.

NAto0df    <- function(x) purrr::map_df(x, ~ replace(.x, is.na(.x), 0)) # For type consistency.

mykable   <- function(df, digits = 2, format.args = mark.list, align = 'r', ...) { # custom kable specifications.
  
  kable(df, 
        digits      = digits, 
        format.args = format.args, 
        align       = align, 
        booktabs    = TRUE, 
        linesep     = '',
        ...)
  
}

myfootnote <- function(..., note) {
  
      footnote(...,
               general_title     = 'Note.',
               general           = note,
               title_format      = 'italic',
               footnote_as_chunk = TRUE)
  
}

report <- function(x, plan_num, except = FALSE, ...) { # Main reporting function
  
  grp.t.df <- x # There originally was a lot of repetitive code. To avoid ruining the structure, we make this assignment.
  
  grp.t.df$Total <- apply(grp.t.df[, -1], 1, sum, na.rm = TRUE) # Transactional dataset is row-oriented (remove date from calculation).
  
  grp.t_sum.m        <- apply(grp.t.df[, 2:NCOL(grp.t.df)], 
                              2, 
                              function(x) sum(x, na.rm = TRUE)) # Get the overall totals
  grp.t_sum.df       <- as.data.frame(t(grp.t_sum.m)) # For kable()
  grp.t_sum.df$Month <- 'TOTAL'
  grp.t_sum.df       <- grp.t_sum.df[, c('Month', not_month(grp.t_sum.df))]
  
  grp.t_gt.df <- rbind(grp.t.df, grp.t_sum.df)
  
  plan_mon <- rep(plan_num, NROW(grp.t_gt.df) - 1)
  
  plan <- c(plan_mon, sum(plan_mon)) # To compare whether we are making the goal.
  
  grp.t_gt.df <- transform(grp.t_gt.df, 
                           Plan = plan,
                           Plan_NET = Total - plan,
                           Plan_PCT = (Total - plan)/plan*100)
  
  if (except == FALSE) {
    
    mykable(NAto0df(grp.t_gt.df), ...)
    
  } else {
    
    pre <- NAto0df(grp.t_gt.df)
    
    mykable(t(pre))
    
  }
  
  
  
  
}
numround <- function(x) round(as.numeric(x), 2)

current_months <- function(x, type) {
 
  if (!type %in% 1:2) {
    
    stop('Type must be 1 (length) or 2 (NCOL - 1).')
    
  } else if (type == 1) {
    
    month.name[1:(length(x))]
    
  } else {
    
    month.name[1:(NCOL(x) - 1)] # -1 to exclude TOTAL.
    
    #month.name[-NCOL(x)]
    
  }
  
} 


```
 

```{r Summaries, echo = FALSE, warning = FALSE}
#### Monthlies ####
  
### Gross Income ###
inc_grp.df           <- aggregate(net ~ month + source, inc.df, sum)
names(inc_grp.df)[3] <- 'atd_inc'
  
### Expenses ###
exp_grp.df           <- aggregate(total ~ month + group, exp.df, sum)
names(exp_grp.df)[3] <- 'expenses'
  
### Net Income ###

## Preparing a proper table of monthly income and expenses
inc_sum.df <- aggregate(cbind(earnings, fees, taxes, 
                              pretax_deductions, posttax_deductions, net) ~ month, 
                        inc.df, 
                        sum)

names(inc_sum.df)[2:4]              <- c('gross_income', 'freelance_fees', 'w2_taxes')
names(inc_sum.df)[NCOL(inc_sum.df)] <- 'atd_inc'

exp_sum.df           <- aggregate(total ~ month, exp.df, sum)
names(exp_sum.df)[2] <- 'expenses'
    
inc_exp.df        <- merge(inc_sum.df, exp_sum.df, by = 'month', all.y = TRUE)
inc_exp.df$inc_op <- with(inc_exp.df, atd_inc - expenses)

    
### Investment ###
inv_sum.df           <- aggregate(investment ~ month, inv.df, sum, na.rm = TRUE)
names(inv_sum.df)[2] <- 'inv'

inv_grp.df           <- aggregate(investment ~ month + source + sub_type, 
                                  inv.df, 
                                  sum, na.rm = TRUE)

```


# A. Financial Summary (Values Randomized)

\pagenumbering{arabic} 

```{r UPSHOT_setup, echo = FALSE}
   options(knitr.kable.NA = '-')

upshot.col <- c('Month', 
                'Gross Income', 
                'Freelance Fees', 
                'W2/Contractor Taxes', 
                'Pre-Tax Deductions',
                'Post-Tax Deductions',
                'Take-Home Pay',
                'After-Income Expenses',
                'Operating Income', 
                'Investment Outflow', 
                'Net Income',
                'Savings')

##### Preparation #####
upshot.df         <- merge(inc_exp.df, inv_sum.df, by = 'month', all.x = TRUE)
upshot.df$ni      <- with(upshot.df, ifelse(is.na(inv), inc_op, inc_op - inv))
upshot.df$savings <- with(upshot.df, ifelse(is.na(inv), inc_op/2, (inc_op - inv)/2))

##### The Table #####
#upshot_sum.m        <- apply(upshot.df[, 2:NCOL(upshot.df)], 2, function(x) sum(x, na.rm = TRUE))
upshot_sum.m        <- mapc(sum, upshot.df[, 2:NCOL(upshot.df)], na.rm = TRUE)
upshot_sum.df       <- as.data.frame(t(sapply(upshot_sum.m, function(x) ifelse(is.na(x), 0, x))))
upshot_sum.df$month <- 'TOTAL'
upshot_sum.df       <- upshot_sum.df[, c('month', not_month(upshot_sum.df))]
  
upshot_gt.df        <- rbind(upshot.df, upshot_sum.df)

colnames(upshot_gt.df) <- upshot.col

upshot_gt.df[, 2:NCOL(upshot_gt.df)] <- sapply(upshot_gt.df[, 2:NCOL(upshot_gt.df)], numround)

upshot2 <- t(upshot_gt.df[, 2:NCOL(upshot_gt.df)])

colnames(upshot2) <- c(current_months(upshot2, 2), 'TOTAL')
                  
```

## Fig. `r f <- 1; f` - Monthly Performance
```{r fig_mp, echo = FALSE, fig.align = 'center', warning = FALSE, fig.align = 'center', fig.height = 3.8, message = FALSE}
## PLOTTING ##
    
# Tidying data into a proper form for graphing #
inc_exp_stack.df        <- stack(inc_exp.df, select = -month)
inc_exp_stack.df$month  <- rep(inc_exp.df$month, length.out = NROW(inc_exp_stack.df))
names(inc_exp_stack.df) <- c('amount', 'category', 'month')
    
# Graphing by category to track financial performance #
inc_exp_sub.df <- subset(inc_exp_stack.df, category %in% c('atd_inc', 'expenses', 'inc_op'))

fig1.gph <- ggplot(inc_exp_sub.df, 
         aes(x = as.integer(month), 
             #x = month2,
             colour = category)) +
  geom_line(aes(y = amount/1000)) +
  labs(x      = 'Month',
       y      = 'Amount, $1000s',
       colour = 'Category') +
  scale_color_manual(labels = c('Take-Home Pay',
                                'Expenses',
                                'Operating Income'),
                     values = c('cyan4', 'salmon', 'forestgreen')) +
  scale_x_continuous(breaks = 1:(NCOL(upshot2) - 1),
                     limits = with(inc.df, c(1, NCOL(upshot2) - 1)))
      
# PRINT PLOT #
fig1.gph + 
  #theme_minimal() +
  theme_light() + 
  #theme_classic() +
  theme(panel.grid.minor.x = element_blank(),
        legend.position = 'bottom')
```

## Fig. `r f <- f + 1; f` - Analysis of Totals
```{r fig_aot, echo = FALSE, fig.height = 3.8, fig.align = 'center'} 
aot_dat <- upshot2[, 1:(NCOL(upshot2) - 1)]

upshot_aot <- transform(as.data.frame(upshot2), 
                        Category = rownames(upshot2),
                        MEDIAN   = mapr(median, aot_dat, na.rm = TRUE),
                        MEAN     = mapr(mean, aot_dat, na.rm = TRUE),
                        SD       = mapr(sd, aot_dat, na.rm = TRUE))




fig_aot2 <- ggplot(upshot_aot, 
                 aes(y = reorder(Category, TOTAL), 
                     x = TOTAL/1000
                     )) +
  geom_point(stat = 'identity', 
             col = 'pink3' # magenta3, palegreen3?
             ) +
  guides(col = FALSE) +
  labs(y = '',
       x = 'Value, $1000s') +
  #scale_x_discrete(labels = scales::comma
                   #breaks = seq(0, max(upshot_mm$Value)+10^3, 10^3)) + 
  theme_light() + 
  #theme_dark() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

fig_aot2

```


## Fig. `r f <- f + 1; f` - Central Tendency Distributions
```{r fig_upm, echo = FALSE, fig.align = 'center', fig.height = 3.6}
upshot_mm <- gather(upshot_aot[, c('Category', 'MEDIAN', 'MEAN')], Metric, Value, 2:3)

fig_mm <- ggplot(upshot_mm, 
                 aes(y = reorder(Category, Value), 
                     x = Value/1000, 
                     col = Metric)) +
  geom_point(stat = 'identity') +
  #geom_bar(stat = 'identity') + # Dots are cleaner.
  facet_wrap(~ Metric) + 
  guides(col = FALSE) +
  labs(y = '',
       x = 'Value, $1000s') +
  #scale_x_discrete(labels = scales::comma
                   #breaks = seq(0, max(upshot_mm$Value)+10^3, 10^3)) + 
  #scale_color_manual(values = c('green3', 'cyan3')) + # For dark theme.
  theme_light() + 
  #theme_dark() + # looks cooler, but uses more ink...
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

fig_mm

```

## Table `r n <- 1; n` - Monthly Summary
```{r UPSHOT_output, echo = FALSE}
upshot_table <- upshot_aot[, !grepl('Category', names(upshot_aot))]

mykable(upshot_table[, 1:8])
mykable(upshot_table[, 9:NCOL(upshot_table)])

```

\newpage

# B. Breakdown (Values Randomized)

## Table `r n <- n + 1; n` - Net Earnings
```{r Income, echo = FALSE}
    options(knitr.kable.NA = '-')

  ### INCOME ###
    inc_grp.t.df       <- spread(inc_grp.df, source, atd_inc)
    inc_grp.t.df$month <- current_months(inc_grp.t.df$month, 1)
    
    names(inc_grp.t.df)[1] <- 'Month'
    
    report(inc_grp.t.df, plan_inc, align = c('l', rep('r', NCOL(inc_grp.t.df)))) #%>%
      #column_spec(NCOL(inc_grp.t.df) + 1, border_right = TRUE)
```


## Table `r n <- n + 1; n` - Expenses
```{r Expenses, echo = FALSE}
   options(knitr.kable.NA = '-')

    exp_grp.t.df  <- NAto0df(spread(exp_grp.df, group, expenses))
    
    #report(exp_grp.t.df[1:6, ], plan_exp, except = TRUE)
    #report(exp_grp.t.df[7:NROW(exp_grp.t.df), ], plan_exp, except = TRUE)
    
    exp_out <- rbind(exp_grp.t.df,
                     c('TOTAL', 
                       sapply(exp_grp.t.df[, not_month(exp_grp.t.df)], sum)))
    
    exp_out[, 2:NCOL(exp_out)] <- sapply(exp_out[, 2:NCOL(exp_out)], numround)
    
    exp_out0 <- transform(exp_out, total = apply(exp_out[, 2:NCOL(exp_out)], 1, sum))
    
    plan_expv <- rep(plan_exp, NROW(exp_out0) - 1) %>%
      c(., sum(.))
    
    exp_out1 <- transform(exp_out0,
                          Plan     = plan_expv,
                          Plan_NET = total - plan_expv,
                          Plan_PCT = (((total - plan_expv)/plan_expv)*100))
    
    exp_out2 <- t(exp_out1)
    
    exp_out3 <- as.data.frame(exp_out2[2:NROW(exp_out2), ])
    
    exp_out4 <- apply(exp_out3, 2, numround)
    
    rownames(exp_out4) <- rownames(exp_out3)
    rownames(exp_out4) <- gsub('total', 'Total', rownames(exp_out4))
    
    colnames(exp_out4) <- c(current_months(exp_out4, 2), 'TOTAL')
    
    #apply(exp_out4[, 1:(NCOL(exp_out4) - 1)], 1, mean, na.rm = TRUE),
    
    exp_out5 <- transform(exp_out4,
                          MEAN   = mapr_nt(exp_out4, mean),
                          MEDIAN = mapr_nt(exp_out4, median),
                          SD     = mapr_nt(exp_out4, sd)
                          )
    
    mykable(exp_out5[, 1:8]) %>%
      row_spec(NROW(exp_out5) - 3, hline_after = TRUE)
    
    mykable(exp_out5[, 9:NCOL(exp_out5)]) %>%
      row_spec(NROW(exp_out5) - 3, hline_after = TRUE)
    
```

\newpage

# C. Donations (Values Randomized)
## Table `r n <- n + 1; n` - Donation Transactions
```{r Donations1, echo = FALSE}
donations <- subset(exp.df, group == 'Donations')

donations2 <- donations[, !grepl('year|qua|month', names(donations))]

donations3 <- donations2[, grepl('date|subgroup|desc|place|price|tax|total', names(donations2))]

donations3$subgroup <- gsub('Non-tax deductible', 'Non-TD', donations3$subgroup)
donations3$subgroup <- gsub('Tax-deductible', 'TD', donations3$subgroup)

donations3[, c('Item_desc', 'place')] %<>%
  map_df(~ gsub('.*', '[REDACTED]', .x))

mykable(donations3, 
        col.names = toupper(names(donations3)),
        align = c('l', rep('r', NCOL(donations3) - 1))) %>%
  kable_styling(full_width = TRUE) %>%
  row_spec(1:(NROW(donations3) - 1), hline_after = TRUE) %>%
  column_spec((NCOL(donations3) - 2):NCOL(donations3), width = '3.5em') %>%
  footnote(general_title     = 'Notes.',
           general           = 'TD = Tax Deductible. "Subgroup" is the grouping under the parent group "Donations."',
           title_format      = 'italic',
           footnote_as_chunk = TRUE)
```

## Table `r n <- n + 1; n` - Donation Totals
```{r Donations2, echo = FALSE}
donations_agg <- aggregate(cbind(price, tax, total) ~ subgroup, donations3, sum, na.rm = TRUE)

donations_agg2 <- do.call(data.frame, donations_agg)

donations_agg2$subgroup %<>% as.character(.)

donations_agg3 <- rbind(donations_agg2, 
                        c('TOTAL', mapnum(sum, donations_agg2)))

donations_agg3[ , 2:NCOL(donations_agg3)] %<>% mapc(numround, .)

mykable(donations_agg3, 
        col.names = c('Type', 'Total Donations', 'Tax', 'Total Payment'),
        align     = c('l', rep('r', NCOL(donations_agg) - 1))) %>%
  footnote(general_title     = 'Notes.',
           general           = 'TD = Tax Deductible; "Subgroup" is the grouping under the parent group "Donations."',
           title_format      = 'italic',
           footnote_as_chunk = TRUE,
           threeparttable    = TRUE)
```

\newpage

# D. Account Balances (Values Randomized)
```{r accounts0, echo = FALSE}
bal <- read.csv('~/MEGA/Personal/Money/balances.csv', stringsAsFactors = FALSE) # Why won't it work without the direct file path? The other imports worked fine?

bal[, 3:NCOL(bal)] %<>% map_rand()

bal2 <- transform(bal, 
                  Year             = substr(date, 1, 4),              # Need to subset Balances data based on the Year.
                  Month            = as.numeric(substr(date, 6, 7)),  # Need to get the most recent record for a particular month.
                  Day              = as.numeric(substr(date, 9, 10)), # Just in case.
                  stringsAsFactors = FALSE,
                  Savings          = bal_savavail)

bal2[, c('bal_savavail', 'bal_savcurr')] <- NULL

### Total of All Accounts
total_accts <- bal2 %>%
  select(grep('Month|^bal|Savings', names(bal2))) %>%
  group_by(Month) %>%
  summarise_all(sum, na.rm = TRUE) %>%
  mutate(Investments = bal_ira + bal_bro + bal_403b) %>%
  mutate(`Net Assets` = bal_chk + Investments - bal_cr) %>%
  mutate(Change = `Net Assets` - lag(`Net Assets`)) %>%
  mutate(Change_Pct = Change/lag(`Net Assets`))

total_accts2 <- total_accts[, c('Month', 'bal_chk', 'Savings', 'Investments', 'bal_cr', 'Net Assets', 'Change', 'Change_Pct')]

```

```{r accounts_function, echo = FALSE}
mykable2 <- function(df, align = c('l', rep('r', NCOL(df) - 1)), row.names = FALSE,...) {
  
  mykable(df, align = align, row.names = row.names, ...)
  
}
```


## Table `r n <- n + 1; n` - Monthly Total Balances
```{r accounts_total, echo = FALSE}
bal_names <- c('Month', 'Checking', 'Savings', 'Investments', 'Credit Liability', 'Net Assets', 'Change', 'Change %')
mykable2(total_accts2, col.names = bal_names)
```

\  

\  

*End of Document*

`r # cat(rep('\\  \n', 4))`

`r # \vspace{1.75in}\textit{End of Document}`