---
title: "Iterative Generation of Frequency Distributions"
author: "Robert Schnitman"
date: "November 21, 2019"
output: pdf_document
---

```{r setup, echo = FALSE}
link <- 'https://www.github.com/robertschnitman/RS_Reports/FD.rmd'
```

# Introduction

The purpose of this document is to demonstrate the how to produce a multi-paged report of frequency distributions via R Markdown. The source code is located at `r link`.

# Code Explanation

## 1. Load libraries.

First, loads some necessary and helpful packages. If exporting to PDF, install `tinytex` and execute `tinytex::install_tinytex()`.
```{r libs}
# install.packages('tinytex')
# tinytex::install_tinytex()
library(knitr)
library(kableExtra)
library(tidyverse)
library(magrittr)
```

## 2. Create a function that generalizes the generation of frequency distributions.

One can obtain counts via `table(...)` and percentages via `prop.table(table(...))`; however, to have both in the same matrix or data frame is not innately possible within R. While there exists packages such as `gmodels` that generate crosstabs, they are not typically `kable`-friendly. Thus, the function below outlines how we can include counts and percentages within the same data frame.

```{r fun_mt}
main_table <- function(...) {
  
 ### Check if the number of variables is not 2.
 ## For now, cross-tabs between two variables is only possible at this point.
 dots <- list(...)
 
 if (length(dots) != 2) {
   
   stop(paste0('This function assumes two variables. Number of variables detected is ', 
               length(dots), 
               '.')) 
   
 }
  
 ### Generate the counts.
 freq <- table(...)
  
 freq_df <- as.data.frame(freq) %>%
   spread(NCOL(.) - 1, NCOL(.)) %>%
   mutate(Total = apply(.[, 2:NCOL(.)], 1, sum))
 
 ### Generate the ROWWISE percentages.
 prop_df <- freq_df
 prop_df[, 2:NCOL(prop_df)] <- prop_df[, 2:NCOL(prop_df)]/prop_df$Total
 prop_df[, 2:NCOL(prop_df)] %<>% 
   map_df(~ paste0(round(.x*100), '%'))
 
 ### Convert freq_df and prop_df into characters so that we can combine them into the same data frame.
 freq_df %<>% # Format the counts so that they are of the NNN,NNN format.
   format(., big.mark = ',', scientific = FALSE) %>%
   map_df(as.character)
 prop_df %<>% map_df(as.character)

 ### Combine freq_df and prop_df
 combine <- map_df(1:NROW(freq_df), ~ rbind(freq_df[.x, ], prop_df[.x, ]))
 
 combine
  
}
```

```{r fun_mk, warnings=FALSE, echo = FALSE}
main_knit <- function(mt, caption) {
 
  mt %>%
    kable('latex', booktabs = TRUE, caption = caption, linesep = '') %>%
    kable_styling(full_width = TRUE) %>%
    collapse_rows(1, valign = "top", latex_hline = "major")
    
  
}
```

```{r tables, results = 'asis', echo = FALSE}
clarities <- unique(diamonds$clarity)

for (i in 1:length(clarities)) {
  
  ss <- subset(diamonds, clarity == clarities[i])
  
  mt <- with(diamonds, main_table(color, cut))
  
  main_knit(mt, paste0('Clarity: ', clarities[i])) %>%
    print()
  
  #cat('\\newpage')
  
}
