---
title: "Econometrics & Statistical Programming Tutor"
author: Robert Schnitman
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

\pagenumbering{gobble}

## About Me

I am an alumnus of the Master of Science in Economics degree program at The University of Texas at Dallas, which is where I also have received my Bachelor of Science in Economics degree. My graduate concentration was applied econometrics. I have worked for JCPenney and Collin College, applying regression methods and writing functions in R. For **$25 per hour** (group rates $20 per hour--all hourly rates negotiable), I can tutor in the following subjects in person or online:

\begin{itemize}

\item \textbf{Quantitative Methods:} Econometrics, Statistics 

\item \textbf{Statistical Computing:} R, Stata 

\item \textbf{Writing:} Research, Proofreading

\end{itemize}

I look forward to helping you!

## Contact Info
214-676-2376  
robertschnitman@gmail.com  
https://www.wyzant.com/Tutors/rsecon  

## Sample Code - Model Comparisons
```{r, fig.height = 2, fig.width = 5, fig.align = 'center'}
split(diamonds, diamonds$color) %>%
  map_df(~ summary(lm(price ~ carat + depth, .x))$adj.r.squared) %>%
  gather(Category, Value, 1:NCOL(.)) %>%
  ggplot(aes(x = Category, y = Value, fill = Category)) + 
    geom_bar(stat = 'identity') + 
    scale_fill_brewer(palette = 'Blues') +
    theme_light() + 
    theme(legend.position    = 'none',
          panel.grid.minor   = element_blank(),
          panel.grid.major.x = element_blank()) + 
    labs(y = 'Adjusted R-Square', x = 'Color Category')
```





