---
name: Robert Schnitman
position: Statistician and Tutor
phone: 214-676-2376
email: "robertschnitman@gmail.com"
#www: "sites.google.com/view/robertschnitman"
github: robertschnitman
linkedin: rschnitman
aboutme: "Experienced Statistical Consultant with a demonstrated history of research and analysis. Skilled in R, Stata, and econometrics. Strong research professional with a master's degree in economics from The University of Texas at Dallas. For consulting needs, my rate is **$30 per hour**. For **$25 per hour** (group rates $20 per hour--all hourly rates negotiable), I can tutor in R, Stata, statistics, and econometrics in person or online."
output: vitae::twentyseconds
---

```{r, include = FALSE}
libs <- c('tidyverse', 'magrittr')

for (i in libs) {
  
  if (!require(i, character.only = TRUE)) {
    
    install.packages(i)
    library(i, character.only = TRUE)
    
  }
  
}
```

# Education
*The University of Texas at Dallas*  
2015 M.S. Economics, 3.704 GPA  
2015 G.C. Economic & Demographic Data Analysis  
2014 B.S.	Economics  

# Experience
## Statistical Consultant | Self-employed
*2016 January – Present*

\begin{itemize}

\item Promoted evidence-based research by writing statistical reports grounded on economic, agricultural, and public health data.

\item Restructured datasets of 10,000+ observations and 100+ variables to ensure the quantitative methods generated valid estimations.

\item Created scatter diagrams and computed regression models to reveal trends between firm revenue and customer demographics.

\item Developed programming scripts in R, Stata, and SPSS to facilitate reproducible results for social scientists.

\item Tutored 200+ hours on WyzAnt in R, Stata, statistics, and econometrics.

\end{itemize}

# Sample Code - Model Comparisons
```{r, fig.height = 2, fig.width = 5, fig.align = 'center'}
diamonds %>%
  split(.$color) %>%
  map(~ lm(price ~ carat + depth, .x)) %>% 
  map(summary) %>%
  map_df('adj.r.squared') %>%
  gather(Category, Value, 1:NCOL(.)) %>%
  ggplot(aes(x = Category, y = Value, fill = Category)) + 
    geom_bar(stat = 'identity') + 
    scale_fill_brewer(palette = 'Blues') +
    theme_light() + 
    theme(legend.position    = 'none',
          panel.grid.minor   = element_blank(),
          panel.grid.major.x = element_blank()) + 
    labs(y = 'Adjusted R-Square', x = 'Color Category')
```





