---
title: "Iterative Generation of Frequency Distributions"
author: "Robert Schnitman"
date: "November 21, 2019"
output: pdf_document
---

```{r setup, echo = FALSE}
link <- 'https://github.com/robertschnitman/RS_Reports/blob/master/FD/FD.rmd'
```

The purpose of this document is to demonstrate the production of a multi-paged report of frequency distributions via R Markdown. What follows is a cross-tabulation between the color and quality of diamonds by their depth level. The data used is `diamonds` from the R library `ggplot2`. 

At a high level, we perform the following to generate the tables in this report:

1. Load table-styling and data management libraries (`knitr`, `kableExtra`, `tidyverse`, and `magrittr`). This step assumes that `tinytex` has been installed in RStudio and that `tinytex::install_tinytex()` has been executed.

2. Create a function that combines the counts and row-wise percentages in their own dataset (more specifically, a `data frame`).

3. Write a function that generalizes the preferred table style: counts and row-wise percentages for each row-group, along with computed means of the quality level.

4. Apply steps 2 and 3 above for each depth level via a `for` loop (i.e. "for each depth level, generate the cross-tabulation between the diamonds' color and quality category").

The source code is located at `r link`.

```{r libs, echo = FALSE, results ='hide', warning = FALSE, messages = FALSE}
# install.packages('tinytex')
# tinytex::install_tinytex()
library(knitr)
library(kableExtra)
suppressMessages(library(tidyverse))
suppressMessages(library(magrittr))
```

```{r fun_mt, echo = FALSE}
main_table <- function(...) {
  
 ### Check if the number of variables is not 2.
 ##  For now, cross-tabs between two variables is only possible at this point.
 dots <- list(...)
 
 if (length(dots) != 2) {
   
   stop(paste0('This function assumes two variables. Number of variables detected is ', 
               length(dots), 
               '.')) 
   
 }
  
 ### Generate the counts and means.
 freq <- table(...)
  
 freq_df <- as.data.frame(freq) %>%
   spread(NCOL(.) - 1, NCOL(.)) %>%
   mutate(Total = apply(.[, 2:NCOL(.)], 1, sum),
          Mean  = apply(.[, 2:NCOL(.)], 1, function(x) round(sum(x*1:5)/sum(x), 2)))
 
 ### Generate the ROWWISE percentages.
 prop_df <- freq_df
 prop_df[, 2:NCOL(prop_df)] <- prop_df[, 2:NCOL(prop_df)]/prop_df$Total
 
 ### Convert freq_df and prop_df into characters so that 
 ##  we can combine them into the same data frame.
 freq_df %<>% # Format the counts so that they are of the NNN,NNN format.
  format(., big.mark = ',', scientific = FALSE) %>%
  map_df(as.character)
 
prop_df[, 2:(NCOL(prop_df))] %<>% 
    map_df(~ paste0(round(.x*100), '%'))
 
 prop_df %<>% 
   map_df(as.character) %>%
   mutate(Mean = '')

 ### Combine freq_df and prop_df
 combine <- map_df(1:NROW(freq_df), ~ rbind(freq_df[.x, ], prop_df[.x, ]))
 
 combine
  
}
```

```{r fun_mk, warnings=FALSE, echo = FALSE}
main_knit <- function(mt, caption, col.names = NA) {
 
  mt %>%
    kable('latex', 
          booktabs = TRUE, 
          caption = caption, 
          linesep = '',
          col.names = col.names) %>%
    kable_styling(full_width = TRUE) %>%
    collapse_rows(1, valign = "top", latex_hline = "major")
    
  
}
```

```{r tables1, results = 'asis', echo = FALSE}
names_clarity <- c('Color',
                   '1 = Fair',
                   '2 = Good',
                   '3 = Very Good',
                   '4 = Premium',
                   '5 = Ideal',
                   'Total',
                   'Mean Quality Level')

clarities <- unique(diamonds$clarity)

for (i in 1:length(clarities)) {
  
  ss <- subset(diamonds, clarity == clarities[i])
  
  mt <- with(ss, main_table(color, cut))
  
  main_knit(mt, paste0('Clarity: ', clarities[i]), col.names = names_clarity) %>%
    print()
  
  #cat('\\newpage')
  
}
```
